---
title: "knapsack_package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knapsack_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab6)
```
## Introduction
The package will contain three different functions for solving what is called the knapsack problem.
The knapsack problem is a discrete optimization problem where we have a knapsack that can take a
limited weight W and we want to fill this knapsack with a number of items i = 1, ..., n, each with a
weight wi and a value vi
. The goal is to find the knapsack with the largest value of the elements added
to the knapsack.This problem is NP-hard, meaning that it is "at least as hard as the hardest problem in
NP" (https://en.wikipedia.org/wiki/NP-hardness). NP is a (fundamental) class of problems for which
there are (currently) no polynomial time algorithms to solve them. It is an open (Millennium Prize)
problem, whether it is or is not possible to solve these problemsin polynomial time.

## Package Overview

### Brute force search

The only solution that is guaranteed to give a correct answer in all situations for the knapsack problem
is using brute-force search, i.e. going through all possible alternatives and return the maximum value
found. This approach is of complexity O(2n) since all possible combinations 2n needs to be evaluated.
Implement a function you call knapsack brute force(x, W) that takes a data.frame cx with two
variables v and w and returns the maximum knapsack value and which elements (rows in the data.frame).
The variable W is the knapsack size.
The function should check that the inputs are correct (i.e. a data.frame with two variables v and w)
with only positive values.
The easiest way to enumerate all different combinations is using a binary representation of the numbers
1 to 2n and include all elements of that is equal to 1 in the binary representation. A function that can
do this for you in R is intToBits(). Below is how the function should work (observe that only the first
couple of objects are studied).

#### Example

brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)

$value

[1] 16770

$elements

[1] 5 8

brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500)

$value

[1] 16770

$elements

[1] 5 8

brute_force_knapsack(x = knapsack_objects[1:8,], W = 2000)

$value

[1] 15428

$elements

[1] 3 8

brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000)

$value

[1] 15428

$elements

[1] 3 8

### Dynamic programming

We will now take another approach to the problem. If the weights are actually discrete values (as in our
example) we can use this to create an algorithm that can solve the knapsack problem exact by iterating
over all possible values of w.
The pseudocode for this algorithm can be found here
https://en.wikipedia.org/wiki/Knapsack problem#0.2F1 knapsack problem. Implement this function as knapsack dynamic(x, W). This function should return the same results as the brute force algorithm, but unlike the brute force it should scale much better since the algorithm will run in O(W n).

### Greedy heuristic

A last approach is to use the a heuristic or approximation for the problem. This algorithm will not give
an exact result (but it can be shown that it will return at least 50% of the true maximum value), but
it will reduce the computational complexity considerably (actually to O(n log n) due to the sorting part
of the algorithm). A short description on how to implement the greedy approach can be found here
(https://en.wikipedia.org/wiki/Knapsack problem#Greedy approximation algorithm). Below is
an example on how the function should work.

#### Example

greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)

$value

[1] 192647

$elements

[1] 92 574 472 80 110 537 332 117 37 776 577 288 234 255 500 794 55 290 436
[20] 346 282 764 599 303 345 300 243 43 747 35 77 229 719 564

greedy_knapsack(x = knapsack_objects[1:1200,], W = 2000)

$value

[1] 212337

$elements

[1] 92 574 472 80 110 840 537 1000 332 117 37 1197 1152 947 904
[16] 776 577 288 1147 1131 234 255 1006 833 1176 1092 873 828 1059 500
[31] 1090 794 1033

### Question

#### Question-1

How much time does it takes to run the algorithm for n = 16 objects?

#### Answer
print(system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3200)))

   user  system elapsed 
   
 178.11   56.69  344.49


#### Question-2

How much time does it takes to run the algorithm for n = 500 objects?

#### Answer
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))

   user  system elapsed 
   
   0.50    0.02    0.80


#### Question-3

How much time does it takes to run the algorithm for n = 1000000 objects?

system.time(greedy_knapsack(x = knapsack_objects[1:8,], W = 3500))

   user  system elapsed 
   
   0.01    0.00    0.02


#### Question-4

What performance gain could you get by trying to improving your code?

#### Answer
As we identify we can remove all combinations which greater than weight of snapsack.But we tryied speedup algorithm by using 
parallelizing the bottlenacks.Then it faster than previuse algorithm.

#### Question-6

What performance gain could you get by parallelizing brute force search?
      speed up execution time
      data analysis part is fast
      improve the reliability of computations
